---
title: "Contratual relationship in transit"
output: html_notebook
---



```{r}
library(dplyr)
library(readxl)
library(purrr)

```



```{r}
contract<-read_excel("C:/Z-Work/Transit project/Transit agency profile/2016 Contractual Relations_0.xlsx",sheet=1)


contract %>% select(`Reporter Contractual Position`, `Type of Contract`,`Primary Feature`) %>% map(~table(.x))

contract %>% distinct(`Contractee Agency Name`) %>% nrow()  #141
contract %>% distinct(`Contractee Company Name`) %>% nrow()  #819

contract %>% group_by(`Contractee Company Name`) %>% summarise(n=n()) %>% arrange(desc(n))

contract %>% select(`Buyer Supplies Vehicles to Seller`,`Buyer Provides Maintenance Facility to Seller`,`Other Public Assets Provided`) %>% map(~table(.x))

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
